Physcraper: A Python package for continually updated gene trees

### 2020-05-23 phylota-overview.Rmd
finished reviewing phylota citations :tada:

    cites phylota as its predecessor and inspiration. the authors mention that phylotaR
    pipeline mimics phylota's pipeline but with improvememnts.

@@

    - the study that present DarwinTree [@meng2015darwintree], the study

@@

    @meng2015sotree, and @meng2014rapidtree, all cite phylota using the exact same

@@

@@

    been developed to mine the massive amount of information stored in GenBank", along with its R version [phylotaR; @bennett2018phylotar] and restez <https://www.rdocumen-tation.org/packages/restez/versions/1.0.0>.

>>>>

    cites phylota as its predecessor and inspiration. The authors mention that phylotaR
    pipeline mimics phylota's pipeline but with improvements.

@@

    - the study that present DarwinTree [@meng2015darwintree], and all derived studies: the study

@@

    @meng2014rapidtree, @meng2015sotree, and @meng2015solution, all cite phylota using the exact same

@@

    - A phylogenetic revision of the Gymnotidae fish (Teleostei: Gymnotiformes),
    uses phylotaR to retrieve seqeunces, but cites phylota as "a pipeline that implements
    BLAST searches to both identify and download sequence clusters for listed taxonomic
    groups to assemble a robust collection of sequences in a reproducible way based
    on publicly-available gene sequences while avoiding selection bias on the part
    of the assembler".

@@

    been developed to mine the massive amount of information stored in GenBank",
    along with its R version [phylotaR; @bennett2018phylotar] and restez <https://www.rdocumen-tation.org/packages/restez/versions/1.0.0>.
    - The phylotastic project [@stoltzfus2013phylotastic] cites phylota as a "phylogeny-related resource providing ways to generate custom species trees *de novo* for downstream use" along with CIPRES.
